A general Nullstellensatz for generalized spaces

### 2019-05-05 paper-qcoh.tex
Explanation of term "quasicoherence"

\begin{thm}\label{thm:quasicoherence}
The generic~$\TT$-model is \emph{quasicoherent} in the following sense:
From the point of view of~$\Set[\TT]$, for any finitely
presentable~$U_\TT$-algebra~$A$ (finitely presentable object in the category
of~$U_\TT$-algebras), the canonical~$U_\TT$-algebra homomorphism
\[ A \longrightarrow (U_\TT)^{\Spec(A)} \]
is an isomorphism.
\end{thm}

% XXX justification name quasicoherent

\begin{proof}The proof of Lemma~\ref{lemma:char-fp-models} is constructive and
thus valid in the internal language of~$\Set[\TT]$. Hence we can apply it,
internally, to the theory~$\ul{\TT}/U_\TT$ to deduce that a~$U_\TT$-algebra~$A$
is finitely presentable if and only if it is isomorphic to a~$U_\TT$-algebra of
the form~$(\ul{\TT}/U_\TT)\langle X | R \rangle$ with~$X$ Bishop-finite and~$R$
Kuratowski-finite.

>>>>

\begin{thm}\label{thm:quasicoherence}
The generic~$\TT$-model is \emph{quasicoherent} in the following sense:
From the point of view of~$\Set[\TT]$, for any finitely
presentable~$U_\TT$-algebra~$A$ (finitely presentable object in the category
of~$U_\TT$-algebras), the canonical~$U_\TT$-algebra homomorphism
\[ A \longrightarrow (U_\TT)^{\Spec(A)},\ x \longmapsto -(x) \]
is an isomorphism.
\end{thm}

We use the term \emph{quasicoherent} in reference to algebraic geometry: For
an~$\affl$-module~$M$ in the big Zariski topos of a scheme~$S$, where~$\affl$
is the functor of points of the affine line over~$S$, there is a
well-established notion of what it means that~$M$ is quasicoherent. This
property can be characterized in the internal language: Such a module~$M$ is
quasicoherent if and only if, from the internal point of view of the big
Zariski topos, the canonical map~$A \otimes_\affl M \to M^{\Spec(A)}$ is an
isomorphism for any finitely
presented~$\affl$-algebra~$A$~\cite[Theorem~18.19]{blechschmidt:phd}.
Specializing to the case~$M = \affl$, we obtain the quasicoherence condition of
Theorem~\ref{thm:quasicoherence}.

\begin{proof}[Proof of Theorem~\ref{thm:quasicoherence}]The proof of
Lemma~\ref{lemma:char-fp-models} is constructive and
thus valid in the internal language of~$\Set[\TT]$. Hence we can apply it,
internally, to the theory~$\ul{\TT}/U_\TT$ to deduce that a~$U_\TT$-algebra~$A$
is finitely presentable if and only if it is isomorphic to a~$U_\TT$-algebra of
the form~$(\ul{\TT}/U_\TT)\langle X | R \rangle$ with~$X$ Bishop-finite and~$R$
Kuratowski-finite.
